Poincar\'e--Friedrichs constants over triangulated domains

### 2024-05-01 main.tex
Update on Overleaf.

\documentclass[a4paper]{amsart}
\usepackage[utf8]{inputenc}
% \usepackage{fullpage}
\input{header}

@@

\section{Triangulations and polytopal shellings}

@@

@@

Let us assume that $p \in [1,\infty]$ and that $\Omega \subseteq \bbR^{n}$ is an open set. 
We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the Poincar\'e--Friedrichs inequality with exponent $p \in [1,\infty]$
if there exists a constant $C_{{\rm PF},\Omega,p} \geq 0$ such that the following holds:
for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
such that $\nabla u = \bff$ and 
\begin{align}\label{math:inequalitypf:gradient}
    \| u \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},\nabla,\Omega,p} 
    \| \bff \|_{L^{p}(\Omega)}
    .
\end{align}
We call $C_{{\rm PF},\Omega,p}$ the Poincar\'e--Friedrichs constant. 
This inequality implies an upper bound for the generalized inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.

\begin{remark}
    Before we proceed, we wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known are Poincar\'e inequality or also Friedrichs inequality in the literature.

    Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, 
    we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
    if there exists $C_{{\varnothing},\Omega,p} \geq 0$ such that 
    for all $u \in W^{1,p}(\Omega)$
    \begin{align}
        \| u - u_{\Omega} \|_{L^{p}(\Omega)}
        \leq 
        C_{\varnothing,\Omega,p} 
        \| \nabla u \|_{L^{p}(\Omega)}
        ,
    \end{align}
    where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
    \begin{align*}
        u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u.
    \end{align*}
    Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{\varnothing,\Omega,p}$. 
    Towards a converse inequality, 
    let us first observe that the average of any $v \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
    \begin{align*}
        \| v_\Omega \|_{L^{p}(\Omega)}^{p}
        = 
        \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)| \right)^{p}
        \leq 
        \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)|^{p} \right)
        = 
        \| v \|_{L^{p}(\Omega)}^{p}
        .
    \end{align*}
    Here, we have used Jensen's inequality. 
    In the case $p = \infty$, any $v \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| v \|_{L^{\infty}(\Omega)}$. 
    We therefore combine 
    \begin{align*}
        \| v - v_\Omega \|_{L^{p}(\Omega)} 
        \leq
        2
        \| v \|_{L^{p}(\Omega)},
        \quad 
        v \in L^{p}(\Omega)
        .
    \end{align*}
    \begin{align*}
        \color{Emerald}
        \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
        \leq 
        2^{p-1} 
        \| u \|_{L^{p}(\Omega)}^{p}
        +
        2^{p-1} 
        \| u_\Omega \|_{L^{p}(\Omega)}^{p}
        \leq 
        2^{p} 
        \| u \|_{L^{p}(\Omega)}^{p}
        .
    \end{align*}
    We conclude that the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with $C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}$. 
    In the special case $p=2$, we always have $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $v \in L^{2}(\Omega)$,
    and therefore it even follows that $C_{\varnothing,\Omega,2} \leq C_{{\rm PF},\Omega,2}$. 
    \color{red} Question: can we modify the preceding discussion for general $p$ so that this special inequality for $p=2$ emerges as a limit case? Then we get stronger results for $p \approx 2$. Stern's paper? \color{black}

    The Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators. 
    The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
    When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
    which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
    \color{red} Make this last paragraph for concise.
\end{remark}

% either proceeding simplex by simplex, matching along faces 
% or proceeding patch by patch, matching over intersections
\begin{theorem}
    \color{red}Precise form of the inequality yet to be discussed, though the construction is clear.
\end{theorem}

@@

>>>>

\documentclass[a4paper]{amsart}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}

@@

\section{Basic notions of triangulations and polytopal shellings}

@@

Given an $n$-dimensional simplicial complex $\calT$, 
we call $n$-simplices $S,T \in \calT$ \emph{strongly connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,T=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$. Clearly, strongly connected in $\calT$ is an equivalence relation. A \emph{strongly connected component} of $\calT$ is an equivalence class under this equivalence relation, and we call $\calT$ strongly connected if it has only one strongly connected component.

@@

Let us assume that $\Omega \subseteq \bbR^{n}$ is an open set. 
Given any $p \in [1,\infty]$, we let $L^p(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^p(\Omega) := L^p(\Omega)^n$ for the corresponding Lebesgue space of vector fields. 
We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.

We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
if there exists a constant $C_{{\rm PF},\Omega,p} \geq 0$ such that the following holds:
for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
such that $\nabla u = \bff$ and 
\begin{align}\label{math:inequalitypf:gradient}
    \| u \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},\Omega,p} 
    \| \bff \|_{L^{p}(\Omega)}
    .
\end{align}
Equivalently, for all $u \in W^{1,p}(\Omega)$ we have 
\begin{align}
    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},\Omega,p} 
    \| \nabla u \|_{L^{p}(\Omega)}
    .
\end{align}
We call $C_{{\rm PF},\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
The main interest in this inequality is that it implies an upper bound for the generalized inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.
\\

Before we proceed, we wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known are Poincar\'e inequality or also Friedrichs inequality in the literature. 
Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, 
we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
if there exists $C_{{\varnothing},\Omega,p} \geq 0$ such that 
for all $u \in W^{1,p}(\Omega)$
\begin{align}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{\varnothing,\Omega,p} 
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
\end{align}
where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
\begin{align*}
    u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u.
\end{align*}
Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{\varnothing,\Omega,p}$. 
Towards a converse inequality, 
let us first observe that the average of any $v \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
\begin{align*}
    \| v_\Omega \|_{L^{p}(\Omega)}^{p}
    = 
    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)| \right)^{p}
    \leq 
    \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)|^{p} \right)
    = 
    \| v \|_{L^{p}(\Omega)}^{p}
    .
\end{align*}
Here, we have used Jensen's inequality. 
In the case $p = \infty$, any $v \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| v \|_{L^{\infty}(\Omega)}$. 
We therefore combine 
\begin{align*}
    \| v - v_\Omega \|_{L^{p}(\Omega)} 
    \leq
    2
    \| v \|_{L^{p}(\Omega)},
    \quad 
    v \in L^{p}(\Omega)
    .
\end{align*}
% \begin{align*}
%     \color{Emerald}
%     \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
%     \leq 
%     2^{p-1} 
%     \| u \|_{L^{p}(\Omega)}^{p}
%     +
%     2^{p-1} 
%     \| u_\Omega \|_{L^{p}(\Omega)}^{p}
%     \leq 
%     2^{p} 
%     \| u \|_{L^{p}(\Omega)}^{p}
%     .
% \end{align*}
Hence the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with $C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}$.

In the special case $p=2$, we always have $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $v \in L^{2}(\Omega)$,
and therefore it even follows that $C_{\varnothing,\Omega,2} \leq C_{{\rm PF},\Omega,2}$. 
This follows from the orthogonality constant functions to average-free functions in $L^2(\Omega)$,
and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).
We use a generalization of the projection estimate that was studied by Stern~\cite{stern2015banach} to obtain improved estimates for all $L^p$ spaces with $1 \leq p \leq \infty$:
since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
\begin{align*}
    \| v - v_\Omega \|_{L^{p}(\Omega)}
    \leq 
    \min\left( 2, 2^{|2/p-1|} \right)
    \| v \|_{L^{p}(\Omega)}
    = 
    2^{|2/p-1|} 
    \| v \|_{L^{p}(\Omega)}
    ,
    \quad 
    v \in L^p(\Omega)
    .
\end{align*}
We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, which reproduces the improved estimate for the Hilbert space case.
The main consequence for us is the estimate 
$C_{\varnothing,\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}$.
\color{red} Question: can the estimate above be further improved for general $p$? Are there known results in the literature? \color{black}

We conclude that our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$.
Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.

\begin{remark}
    Let us further remark why the above notion of Poincar\'e--Friedrichs inequality suits our discussion better than the Poincar\'e inequality. 
    We want to generalize the discussion to the curl and divergence operators. 
    The kernel of the gradient is the one-dimensional space of constant functions, and is thus complemented in the Lebesgue spaces with a canonical choice of projection. 
    By contrast, the curl and divergence operators have infinite-dimensional kernels. 
    Hence, it is not clear a priori whether these kernels are complemented subspaces and admit a projection onto them, not to mention a canonical projection. 
    % The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
    % When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
    % which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
\end{remark}

% See the collection at Lemma 3.24
% https://hal.science/hal-03226049/file/volI_hal.pdf

We now collect examples for Poincar\'e--Friedrich inequalities for important special cases. Over convex bounded domains, it is known~\cite{bebendorf2003note} that 
\begin{align}
    \| u - u_{\Omega} \|_{L^{2}(\Omega)}
    \leq 
    \frac{d}{\pi}
    \| \nabla u \|_{L^{2}(\Omega)}
    ,
    \quad 
    u \in W^{1,2}(\Omega)
    .
\end{align}
More generally~\cite[Theorem~1]{esposito2013poincare}, when $2 \leq p < \infty$, one can show that 
\begin{align}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    \frac{d}{\sqrt[p]{\pi_p}}
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where 
\begin{align}
    \pi_p
    :=
    2\pi \frac{ \sqrt[p]{p-1} }{ p \sin(\pi/p) }
    .
\end{align}
Moreover, we are aware of~\cite{chua2006estimates}, who estimate when $1 < p < \infty$,
\begin{align}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm CW},p}
    d
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where, 
\begin{align}
    C_{{\rm CW},p} 
    := 
    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
    \frac{ 
        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
    }{ 
        \| \nabla v \|_{L^{p}([0,1])} 
    }
    \leq 
    \sqrt[p]{p} 2^{1-\frac 1 p}
    .
\end{align}

% https://www.ams.org/journals/proc/2004-132-01/S0002-9939-03-07004-7/S0002-9939-03-07004-7.pdf
% d/2 in the case $p = 1$ over convex domains

% https://academic.oup.com/plms/article/93/1/197/1462187
% they formally require that f is Lipschitz. But convex domains are Lipschitz and hence Lipschitz is dense in all Sobolev spaces, right?

% either proceeding simplex by simplex, matching along faces 
% or proceeding patch by patch, matching over intersections
\begin{theorem}
    \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
\end{theorem}

@@

% https://people.tamu.edu/~guermond//PUBLICATIONS/ern_guermond_m2an_2016.pdf 
% Lemma 5.5
